# Online Community

The genomic data science community is a remarkably open community that continually strives to increase opportunitites and broaden access to the scientific enterprise (e.g. [GDSCN 2022](https://pubmed.gov/35858750){target="_blank"}).
There are many opportunities to interact online with scientists that share a common research question, career stage, or even favorite tool!
Below is a sampling of some discussion forums that you may find useful:

- [help.c-moor.org](https://help.c-moor.org){target="_blank"} for help with and example miniCUREs
- [help.galaxyproject.org](https://help.galaxyproject.org){target="_blank"} for all things Galaxy
- [support.bioconductor.org](https://support.bioconductor.org){target="_blank"} for all things R/Bioconductor
- [help.anvilproject.org](https://help.anvilproject.org){target="_blank"} for interactions with the GDSCN BioDIGS consotrium

```{r, echo=FALSE, fig.alt=''}
ottrpal::include_slide("https://docs.google.com/presentation/d/1fH9s5OLcRF5meZtFWTJe89RFvJSh125kdjhdqp5smqA/edit#slide=id.g302b08c5e6e_0_16")
```

```{r, echo=FALSE, fig.alt=''}
ottrpal::include_slide("https://docs.google.com/presentation/d/1fH9s5OLcRF5meZtFWTJe89RFvJSh125kdjhdqp5smqA/edit#slide=id.g302b08c5e6e_0_5")
```

```{r, echo=FALSE, fig.alt=''}
ottrpal::include_slide("https://docs.google.com/presentation/d/1fH9s5OLcRF5meZtFWTJe89RFvJSh125kdjhdqp5smqA/edit#slide=id.g302b08c5e6e_0_22")
```

```{r, echo=FALSE, fig.alt=''}
ottrpal::include_slide("https://docs.google.com/presentation/d/1fH9s5OLcRF5meZtFWTJe89RFvJSh125kdjhdqp5smqA/edit#slide=id.g302b08c5e6e_0_12")
```
